---
title: "Vignette Title"
author: "Kathy Zhao"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# PACKAGE powers

The goal of powers is to serve as the homework of STAT547M.

## Functions Summary

This package include following functions, 
- squre(): take the square of a vector; 
- boxcox(): take the boxcox transformations of a vector,
- boxcox.inv(): take the inverse boxcox transformations of a vector,
- na.filter(): filter out NA values by row or columns specified by the user for a dataset

## Installation

``` {r, warning = FALSE}
devtools::install_github("zxkathy/powers")
library(powers)
```

## Quick Guide

####1. Function of `square()`

```{r}
square(4)
square(c(1:3))
square(TRUE)
```
As we expected, the square function works well in the vector or number forms. Let's try another one.

```{r, error=TRUE}
square("x")
m <- data.frame(cbind(c(1,2), c(3,4)))
class(m)
square(m)
```
The square function only works in forms of vector of numeric, so it won't work for both str `"x"` and data.frame `m`.

####2. Function of `boxcox()` and `boxcox.inc()`
```{r}
boxcox(2, lambda = 3)
boxcox(1:3, lambda = 0)
```

```{r}
boxcox.inv(2, lambda = 3)
boxcox.inv(1:3, lambda = 0)
```

The above `boxcox()` formula was obtained from the [link](http://onlinestatbook.com/2/transformations/box-cox.html). It doesn't specify the range of `lambda` and `x`, so when I get the case of boxcox result is 0, its inverse should be `Inf`.

Additionally, the above `boxcox.inv()` relies on the function of `boxcox()`. It basically just takes the inverse of the result of `boxcox()`.

```{r, error=TRUE}
boxcox(-1, 0)
```
